---
title: "Prawn aquaculture model numeric estimation of max cumulative profit"
author: "Chris Hoover"
date: "October 4, 2018"
output: 
  pdf_document:
    toc: TRUE
    toc_depth: 3
geometry: margin = 0.5in    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

require(deSolve)
require(sensitivity)
require(parallel)
require(kableExtra)
require(broom)
require(directlabels)
require(furrr)
require(tidyverse)

multiplot <- function(..., plotlist=NULL, file, cols=1, layout=NULL) {
    library(grid)
    
    # Make a list from the ... arguments and plotlist
    plots <- c(list(...), plotlist)
    
    numPlots = length(plots)
    
    # If layout is NULL, then use 'cols' to determine layout
    if (is.null(layout)) {
      # Make the panel
      # ncol: Number of columns of plots
      # nrow: Number of rows needed, calculated from # of cols
      layout <- matrix(seq(1, cols * ceiling(numPlots/cols)),
                       ncol = cols, nrow = ceiling(numPlots/cols))
    }
    
    if (numPlots==1) {
      print(plots[[1]])
      
    } else {
      # Set up the page
      grid.newpage()
      pushViewport(viewport(layout = grid.layout(nrow(layout), ncol(layout))))
      
      # Make each plot, in the correct location
      for (i in 1:numPlots) {
        # Get the i,j matrix positions of the regions that contain this subplot
        matchidx <- as.data.frame(which(layout == i, arr.ind = TRUE))
        
        print(plots[[i]], vp = viewport(layout.pos.row = matchidx$row,
                                        layout.pos.col = matchidx$col))
      }
    }
  }

#Function from stack overflow (https://stackoverflow.com/questions/11693599/alternative-to-expand-grid-for-data-frames)  
  expand.grid.df <- function(...) Reduce(function(...) merge(..., by=NULL), list(...))

# Number of years to simulate
  years = 10

```

# Numeric estimation of max profit  
For each prawn species, shows trajectories of length, density, number of harvests, and cumulative profits over time over a range of stocking densities.

## Find management strategy (stocking density and harvest time) that maximizes profit for each species   
Use function `sim_aqua_eum` to simulate aquaculture cycle with given parameters and starting conditions and return row from the simulation data frame that contains maximum cumulative profits

```{r Opt_stock, cache = TRUE}
source('../R/Prawn_aquaculture/prawn_aquaculture_mod.R')
source('../R/Prawn_aquaculture/prawn_aquaculture_sim.R')
source("../Data/aquaculture_parameters.R")
source("../Data/Ranjeet_Kurup_06_data.R")

  eta.lm = lm(marketable ~ dens, data = rk06)

#Simulation for eumetric curve for M. volenhovenii #####
# Create matriz with parameter sets and stocking densities ranging from 0.5-7.5Pm^-2 
#Starting length of 40 mm corresponds to juveniles of ~0.35 grams
opt.df = expand.grid.df(data.frame(t(par.aqua), c = cost, fc = 0, p = price, delta = delta), 
                        data.frame(L_nought = 40, P_nought = seq(500, 7500, 100))) 

#Get mgmt strategy that maximizes cumulative ten year profits
opt.vol.df <- opt.df %>% bind_cols(pmap_df(., sim_aqua_eum, species = "M. vollenhovenii"))
  opt.vol <- opt.vol.df %>% filter(cum_profits == max(cum_profits))
  
opt.ros.df <- opt.df %>% bind_cols(pmap_df(., sim_aqua_eum, species = "M. rosenbergii"))
  opt.ros <- opt.ros.df %>% filter(cum_profits == max(cum_profits))

eum_dat <- rbind(opt.vol.df, opt.ros.df)  

```

## Simulate full aquaculture cycle through time for a variety of stocking densities to show aquaculture dynamics through time and visualization of the numeric procedure for identifying optimal management conditions  
Use function `sim_aqua_time` which simulates aquaculture cycle through time and returns data frame of the simulation

```{r aqua_sims, warning=FALSE, cache = TRUE}
test_p0s <- seq(500, 7500, 50)  

aqua_sims_vol <- map_df(test_p0s, sim_aqua_time)
aqua_sims_ros <- map_df(test_p0s, sim_aqua_time, species = "M. rosenbergii")

aqua_sims <- bind_rows(aqua_sims_vol, aqua_sims_ros) %>% 
  gather(key = "Variable", value = "Value", P_dens, L, harvest_mass, profit, n_harvest, cum_profits)

```

## Plot showing aquaculture dynamics through time across a variety of stocking densities  
```{r numeric_plot, fig.height=8.5, fig.width=8}
  aqua_sims %>% 
    filter(Variable %in% c("P_dens", "L", "n_harvest", "profit") &
             P_start %in% c(seq(500,7500, 1000)/1000)) %>% 
    mutate(Variable = case_when(Variable == "P_dens" ~ "Density (P)",
                                Variable == "L" ~ "Average Length (mm)",
                                Variable == "n_harvest" ~ "Number of harvests",
                                Variable == "profit" ~ "Profit (USD)")) %>% 
    ggplot(aes(x = time, y = Value, col = as.factor(P_start))) +
      geom_line(size = 1.25) +
      scale_color_manual(name = expression(P[0]),
                         values = c("gray90", "gray80", "red",
                                    "gray60", "gray50", "gray40",
                                    "gray30", "gray20")) +
      facet_grid(Variable ~ Species, scales = "free_y", switch = "y") +
      theme_bw() + 
      theme(axis.text = element_text(size = 12),  #increase axis label size
            axis.title = element_text(size = 18), #increase axis title size
            legend.title = element_text(size = 18), #increase axis title size
            legend.text = element_text(size = 15),#increase legend text size
            strip.text = element_text(size = 14))

```

```{r save_numeric_plot, include = FALSE}
  aqua_sims %>% 
    filter(Variable %in% c("P_dens", "L", "n_harvest", "profit") &
             P_start %in% c(seq(500,7500, 1000)/1000)) %>% 
    mutate(Variable = case_when(Variable == "P_dens" ~ "Density (P)",
                                Variable == "L" ~ "Average Length (mm)",
                                Variable == "n_harvest" ~ "Number of harvests",
                                Variable == "profit" ~ "Profit (USD)")) %>% 
    ggplot(aes(x = time, y = Value, col = as.factor(P_start))) +
      geom_line(size = 1.25) +
      scale_color_manual(name = expression(P[0]),
                         values = c("gray90", "gray80", "red",
                                    "gray60", "gray50", "gray40",
                                    "gray30", "gray20")) +
      facet_grid(Variable ~ Species, scales = "free_y", switch = "y") +
      theme_bw() + 
      theme(axis.text = element_text(size = 12),  #increase axis label size
            axis.title = element_text(size = 18), #increase axis title size
            legend.title = element_text(size = 18), #increase axis title size
            legend.text = element_text(size = 15),#increase legend text size
            strip.text = element_text(size = 14))

ggsave("Figures/numeric_estimation_max_profit.png",
       width = 8, height = 10.5, units = "in")

```

## Heat map showing cumulative profits across parameters representing the two key management decisions: stocking density and when to harvest. Contour lines added to show regions of labeled profits  
```{r time_p0_cumprof_heatmap, fig.height=8, fig.width=8}
cumprof_heatmap <- bind_rows(aqua_sims_vol, aqua_sims_ros) %>% 
  ggplot(aes(y = time, x = P_start, z = cum_profits)) + 
    geom_tile(aes(fill = cum_profits)) + 
    geom_contour(breaks = c(seq(0,6000,1500)), col = "black") +
    geom_dl(aes(label = ..level..), method = "top.pieces",
            stat = "contour", breaks = c(seq(0,6000,1500))) +
    scale_fill_distiller(palette = "Spectral", direction = 1) +
    #scale_fill_gradient2(high = "blue", mid = "bisque",low = "red", breaks = c(-10000, -5000, seq(0,6000,1500))) +
    facet_wrap(~Species, nrow = 2) +
    xlab(expression(paste("Stocking density (",P[0],")", sep = ""))) +
    ylab("Time (days)") +
    theme_bw() + 
      theme(axis.text = element_text(size = 12),  #increase axis label size
            axis.title = element_text(size = 18), #increase axis title size
            legend.title = element_text(size = 15), #increase axis title size
            legend.text = element_text(size = 12),#increase legend text size
            strip.text = element_text(size = 15)) +
    guides(fill=guide_legend(title="Cumulative \nProfits",
                             reverse = T))

cumprof_heatmap
```

```{r save_time_p0_cumprof_heatmap, include=FALSE}
cumprof_heatmap

ggsave("Figures/time_p0_cumprof_heatmap.png",
       width = 6, height = 6, units = "in")

```

# Example aquaculture cycle dynamics run through two years  
Figure showing prawn aquaculture dynamics through time for optimal stocking and harvesting parameters identified from numeric simulation above, vertical dashed lines indicate optimal harvest time for each species  

```{r sim_time_fig, warning = FALSE, fig.height=6, fig.width=8}
# First get simulation through time starting at optimal stocking density ######
opt.vol.time <- sim_aqua_time(opt.vol$P_nought)
opt.ros.time <- sim_aqua_time(opt.ros$P_nought, species = "M. rosenbergii")

  opt.time <- rbind(as.data.frame(opt.vol.time), as.data.frame(opt.ros.time)) %>% 
    mutate(n_harvest = ifelse(as.numeric(as.character(p_mass)) >= 30, as.numeric(as.character(n_harvest)), NA),
           cum_profits = as.numeric(as.character(n_harvest)) * as.numeric(as.character(profit))) %>% 
    gather(key = "Variable", value = "Value", P_dens, L, harvest_mass, profit, n_harvest, cum_profits)

    opt.time %>% mutate(time = as.numeric(time),
                        Value = as.numeric(Value),
                        Species = factor(Species, levels = c("M. rosenbergii", "M. vollenhovenii"))) %>% 
      filter(Variable %in% c("P_dens", "L", "harvest_mass", "cum_profits")) %>% 
      mutate(Variable = case_when(Variable == "P_dens" ~ "Density, P",
                                  Variable == "L" ~ "Mean Length, L (mm)",
                                  Variable == "harvest_mass" ~ "Harvest mass (kg)",
                                  Variable == "cum_profits" ~ "Ten-year Cumulative profit (USD)")) %>% 
      ggplot(aes(x = time, y = Value, col = Species)) +
        geom_line(size = 1.25) +
        geom_vline(xintercept = opt.vol$time, lty = 2, size = 1.1) +
        geom_vline(xintercept = opt.ros$time, lty = 3, size = 1.1) +
        scale_color_manual(values = c("red", "blue")) +
        facet_wrap( ~ Variable, scales = "free_y", nrow = 2) +
        labs(x = "Time (days)") +
        theme_bw() + 
        theme(legend.position = c(0.3, 0.8),
              axis.text = element_text(size = 12),  #increase axis label size
              axis.title = element_text(size = 18), #increase axis title size
              legend.title = element_blank(), #increase axis title size
              strip.text = element_text(size = 14))

```

```{r save_sim_time_fig, include = FALSE}
  opt.time <- rbind(as.data.frame(opt.vol.time), as.data.frame(opt.ros.time)) %>% 
    mutate(n_harvest = ifelse(as.numeric(as.character(p_mass)) >= 30, as.numeric(as.character(n_harvest)), NA),
           cum_profits = as.numeric(as.character(n_harvest)) * as.numeric(as.character(profit))) %>% 
    gather(key = "Variable", value = "Value", P_dens, L, harvest_mass, profit, n_harvest, cum_profits)

    opt.time %>% mutate(time = as.numeric(time),
                        Value = as.numeric(Value),
                        Species = factor(Species, levels = c("M. rosenbergii", "M. vollenhovenii"))) %>% 
      filter(Variable %in% c("P_dens", "L", "harvest_mass", "cum_profits")) %>% 
      mutate(Variable = case_when(Variable == "P_dens" ~ "Density, P",
                                  Variable == "L" ~ "Mean Length, L (mm)",
                                  Variable == "harvest_mass" ~ "Harvest mass (kg)",
                                  Variable == "cum_profits" ~ "Ten-year Cumulative profit (USD)")) %>% 
      ggplot(aes(x = time, y = Value, col = Species)) +
        geom_line(size = 1.25) +
        geom_vline(xintercept = opt.vol$time, lty = 2, size = 1.1) +
        geom_vline(xintercept = opt.ros$time, lty = 3, size = 1.1) +
        scale_color_manual(values = c("red", "blue")) +
        facet_wrap( ~ Variable, scales = "free_y", nrow = 2) +
        labs(x = "Time (days)") +
        theme_bw() + 
        theme(legend.position = c(0.3, 0.8),
              legend.text = element_text(size = 12),
              axis.text = element_text(size = 12),  #increase axis label size
              axis.title = element_text(size = 18), #increase axis title size
              legend.title = element_blank(), #increase axis title size
              strip.text = element_text(size = 14))

    ggsave("Figures/example_aquaculture_simulations.png",
           height = 8, width = 8, units = "in")
```

# Eumetric curves   
Use simulations above across stocking densities that return model parameters at max cumulative profit to plot eumetric curve showing cumulative profits across stocking densities as well as per-harvest profits, harvest time, and number of harvests within `r print(years)` time frame  

## Eumetric curve and associated parameters  
```{r Fig3, warning = FALSE, fig.height=10.5, fig.width=8}
  eum_crv = ggplot(eum_dat, aes(x = P_nought/1000)) +
              theme_bw() +
              theme(legend.position = c(0.2, 0.1),        #place legend inside plot
                    axis.text = element_text(size = 15),  #increase axis label size
                    axis.title = element_text(size = 18), #increase axis title size
                    legend.text = element_text(size = 12),#increase legend text size
                    axis.title.x = element_blank(),       #Suppress x axis since it shares it with below plot
                    axis.text.x = element_blank(),
                    legend.title = element_blank())  +    #suppress legend title
              geom_line(aes(y = cum_profits/1000, col = Species), size = 1.25) +
              scale_color_manual(values = c("red", "blue")) +
              geom_hline(yintercept = 0, aes(col = grey20)) +
              annotate("text", x = 0, y = max(eum_dat$cum_profits), label = "A)", size = 8) +
              labs(y = expression(paste('10-Year Profits, ', CP^sp, ' (1000s USD)', sep = "")))  +
              scale_y_continuous(limits = c(min(eum_dat$cum_profits), 12500)/1000,
                                 breaks = seq(-2.500, 12.500, 2.500)) +
              scale_x_continuous(limits = c(0, 8),
                                 breaks = c(0, 2, 4, 6, 8))  
 
  prf_crv = ggplot(eum_dat, aes(x = P_nought/1000)) +
              theme_bw() +
              theme(legend.position = 'none',        #place legend inside plot
                    axis.text = element_text(size = 15),  #increase axis label size
                    axis.title = element_text(size = 18), #increase axis title size
                    legend.text = element_text(size = 12),#increase legend text size
                    axis.title.x = element_blank(),       #Suppress x axis since it shares it with below plot
                    axis.text.x = element_blank(),
                    legend.title = element_blank())  +    #suppress legend title
              geom_line(aes(y = profit, col = Species), size = 1.25) +
              scale_color_manual(values = c("red", "blue")) +
              geom_hline(yintercept = 0, aes(col = grey20)) +
              annotate("text", x = 0, y = max(eum_dat$profit), label = "B)", size = 8) +
              labs(y = expression(paste('Profit per cycle (USD)', sep = "")))  +
              scale_y_continuous(limits = c(-400, 410),
                                 breaks = seq(-400, 400, 200)) +
              scale_x_continuous(limits = c(0, 8),
                                 breaks = c(0, 2, 4, 6, 8))  

   
eum_time = ggplot(eum_dat, aes(x = P_nought/1000)) +
            theme_bw() +
            theme(legend.position = 'none',        #place legend inside plot
                  axis.text = element_text(size = 15),  #increase axis label size
                  axis.title = element_text(size = 18), #increase axis title size
                  axis.title.x = element_blank(),       #Suppress x axis since it shares it with below plot
                  axis.text.x = element_blank(),
                  legend.text = element_text(size = 12),#increase legend text size
                  legend.title = element_blank())  +    #suppress legend title
            geom_line(aes(y = time, col = Species), size = 1.25) +
            annotate("text", x = 0, y = 365, label = "C)", size = 8) +
            scale_color_manual(values = c("red", "blue")) +
            labs(y = expression(paste('Harvest time, ', T[opt]^sp, ' (days)', sep = "")))  +
            scale_y_continuous(limits = c(0, 365),
                               breaks = c(0,60,120,180,240,300,365)) +
            scale_x_continuous(limits = c(0, 8),
                               breaks = c(0, 2, 4, 6, 8))  

eum_harvests = ggplot(eum_dat, aes(x = P_nought/1000)) +
            theme_bw() +
            theme(legend.position = 'none',        #place legend inside plot
                  axis.text = element_text(size = 15),  #increase axis label size
                  axis.title = element_text(size = 18), #increase axis title size
                  legend.text = element_text(size = 12),#increase legend text size
                  legend.title = element_blank())  +    #suppress legend title
            geom_line(aes(y = n_harvest, col = Species), size = 1.25) +
            annotate("text", x = 0, y = 25, label = "D)", size = 8) +
            scale_color_manual(values = c("red", "blue")) +
            labs(x = expression(paste('Stocking density, ', P[0],' (', Pm^-2, ")", sep = "")), 
                 y = "Harvests per 10 years")  +
            scale_y_continuous(limits = c(0, 30),
                               breaks = c(0,10,20,30),
                               labels = c("0", "10", "20", "  30")) +
            scale_x_continuous(limits = c(0, 8),
                               breaks = c(0, 2, 4, 6, 8))  


  
  eum.layout = matrix(c(1,2,3), ncol = 1, byrow = T)

  multiplot(eum_crv, prf_crv, eum_harvests, layout = eum.layout)

```

## Eumetric curve with uncertainty  
We want to add estimates of uncertainty to the eumetric curve rather than just the eumetric curve generated from point estimates of all parameters (above). We'll use parameter sets from the latin hypercube generated for the PRCC sensitivity analysis to run the model over all tested stocking densities 

```{r Fig3_sensitivity, cache = TRUE}
source("../Data/snail_epi_parameters.R")
source("../Data/combined_parameters.R")

source("../R/Sensitivity_Analysis/sensitivity_prep.R")

par.all = c(par.aqua, par.snails.imm, par.epi_prawn)

# Get aquaculture parameters from LHC
  lhcpars.aqua = lhcpars[,which(colnames(lhcpars) %in% 
                                  c(names(par.aqua), 'k.ros', 'c', 'fc', 'p', 'delta'))]
    lhcpars.aqua$fc <- 0  #No consideration of fixed costs in default model
    
# Get the stocking densities and starting length again
  test_starts <- expand.grid(L_nought = 40, P_nought = seq(500, 7500, 100))
  
# Data frame of all parameter sets and all candidate stocking densities  
  eum_sim <- expand.grid.df(lhcpars.aqua, test_starts)
  
#Simulate across all parameter sets and stocking densities  
  plan(multiprocess)
  eum_sims_vol <- eum_sim %>% 
    bind_cols(future_pmap_dfr(., sim_aqua_eum, species = "M. vollenhovenii"))
  
    eum_sims_vol_sum <- eum_sims_vol %>%       #Summarise across parameter sets
      group_by(P_nought) %>%  
      summarise(Profit_Cycle_Med = median(profit),
                Profit_Cycle_upq = quantile(profit, 0.75),
                Profit_Cycle_loq = quantile(profit, 0.25),
                cum_Profit_Med = median(cum_profits),
                cum_Profit_min = min(cum_profits),
                cum_Profit_max = max(cum_profits),
                cum_Profit_upq = quantile(cum_profits, 0.75),
                cum_Profit_loq = quantile(cum_profits, 0.25),
                Harvest_time_med = median(time),
                Harvest_time_upq = quantile(time, 0.75),
                Harvest_time_loq = quantile(time, 0.25),
                n_harvest_med = median(n_harvest),
                n_harvest_upq = quantile(n_harvest, 0.75),
                n_harvest_loq = quantile(n_harvest, 0.25),
                Species = unique(Species),
                n_par_sets = n())
    
  eum_sims_ros <- eum_sim %>% bind_cols(pmap_df(., sim_aqua_eum, species = "M. rosenbergii"))
  
    eum_sims_ros_sum <- eum_sims_ros %>%       #Summarise across parameter sets
      group_by(P_nought) %>%  
      summarise(Profit_Cycle_Med = median(profit),
                Profit_Cycle_upq = quantile(profit, 0.75),
                Profit_Cycle_loq = quantile(profit, 0.25),
                cum_Profit_Med = median(cum_profits),
                cum_Profit_min = min(cum_profits),
                cum_Profit_max = max(cum_profits),
                cum_Profit_upq = quantile(cum_profits, 0.75),
                cum_Profit_loq = quantile(cum_profits, 0.25),
                Harvest_time_med = median(time),
                Harvest_time_upq = quantile(time, 0.75),
                Harvest_time_loq = quantile(time, 0.25),
                n_harvest_med = median(n_harvest),
                n_harvest_upq = quantile(n_harvest, 0.75),
                n_harvest_loq = quantile(n_harvest, 0.25),
                Species = unique(Species),
                n_par_sets = n())
  
  eum_sims_all_sum = as.data.frame(rbind(eum_sims_vol_sum, eum_sims_ros_sum)) %>% 
    mutate(Species = factor(Species, levels = c("M. rosenbergii", "M. vollenhovenii")))
```

```{r Fig3_with_uncertainty, warning = FALSE, fig.height=10.5, fig.width=8}
  eum_crv2 = eum_sims_all_sum %>% 
    ggplot(aes(x = P_nought/1000, y = cum_Profit_Med/1000, col = Species)) + 
      geom_line(size = 1.25) +
      geom_ribbon(aes(x = P_nought/1000, ymin = cum_Profit_loq/1000, ymax = cum_Profit_upq/1000, fill = Species), alpha = 0.3, size = 0) +
      theme_bw() +
      theme(legend.position = c(0.2, 0.11),        #place legend inside plot
            legend.background = element_rect(fill = "transparent"),
            axis.text = element_text(size = 15),  #increase axis label size
            axis.title = element_text(size = 18), #increase axis title size
            legend.text = element_text(size = 12),#increase legend text size
            axis.title.x = element_blank(),       #Suppress x axis since it shares it with below plot
            axis.text.x = element_blank(),
            legend.title = element_blank())  +    #suppress legend title
      scale_color_manual(values = c("red", "blue")) +
      geom_hline(yintercept = 0, aes(col = grey20)) +
      annotate("text", x = 0, y = 12.5, label = "A)", size = 8) +
      labs(y = expression(paste('10-Year Profits', ' (1000s USD)', sep = "")))  +
      scale_y_continuous(limits = c(-3000, 12750)/1000,
                         breaks = seq(-2.500, 12.500, 2.500),
                         labels = paste("", seq(-2.500, 12.500, 2.500))) +
      scale_x_continuous(limits = c(0, 8),
                         breaks = c(0, 2, 4, 6, 8))  

  prf_crv2 = eum_sims_all_sum %>% 
    ggplot(aes(x = P_nought/1000, y = Profit_Cycle_Med, col = Species)) + 
      geom_line(size = 1.25) +
      geom_ribbon(aes(x = P_nought/1000, ymin = Profit_Cycle_loq, ymax = Profit_Cycle_upq, fill = Species), alpha = 0.3, size = 0) +
      theme_bw() +
      theme(legend.position = "none",        #place legend inside plot
            axis.text = element_text(size = 15),  #increase axis label size
            axis.title = element_text(size = 18), #increase axis title size
            legend.text = element_text(size = 12),#increase legend text size
            axis.title.x = element_blank(),       #Suppress x axis since it shares it with below plot
            axis.text.x = element_blank(),
            legend.title = element_blank())  +    #suppress legend title
      scale_color_manual(values = c("red", "blue")) +
      geom_hline(yintercept = 0, aes(col = grey20)) +
      annotate("text", x = 0, y = 500, label = "B)", size = 8) +
      labs(y = expression(paste('Profit per cycle (USD)', sep = "")))  +
      scale_y_continuous(limits = c(-550, 550),
                         breaks = seq(-500, 500, 250)) +
      scale_x_continuous(limits = c(0, 8),
                         breaks = c(0, 2, 4, 6, 8))  


  eum_time2 = eum_sims_all_sum %>% 
    ggplot(aes(x = P_nought/1000, y = Harvest_time_med, col = Species)) +
      geom_line(size = 1.25) +
      geom_ribbon(aes(x = P_nought/1000, ymin = Harvest_time_loq, ymax = Harvest_time_upq, fill = Species), alpha = 0.3, size = 0) +
      theme_bw() +
      theme(legend.position = 'none',    
            axis.text = element_text(size = 15),  #increase axis label size
            axis.title = element_text(size = 18), #increase axis title size
            axis.title.x = element_blank(),       #Suppress x axis since it shares it with below plot
            axis.text.x = element_blank(),
            legend.text = element_text(size = 12),#increase legend text size
            legend.title = element_blank())  +    #suppress legend title
      annotate("text", x = 0, y = 365, label = "B)", size = 8) +
      scale_color_manual(values = c("red", "blue")) +
      labs(expression(paste('Harvest time, ', T[opt]^sp, ' (days)', sep = "")))  +
      scale_y_continuous(limits = c(0, 365),
                         breaks = c(0,60,120,180,240,300,365)) +
      scale_x_continuous(limits = c(0, 8),
                         breaks = c(0, 2, 4, 6, 8))  

  eum_harvests2 = eum_sims_all_sum %>% 
    ggplot(aes(x = P_nought/1000, y = n_harvest_med, col = Species)) +
      geom_line(size = 1.25) +
      geom_ribbon(aes(x = P_nought/1000, ymin = n_harvest_loq, ymax = n_harvest_upq, fill = Species), alpha = 0.3, size = 0) +
      theme_bw() +
      theme(legend.position = 'none',        #place legend inside plot
            axis.text = element_text(size = 15),  #increase axis label size
            axis.title = element_text(size = 18), #increase axis title size
            legend.text = element_text(size = 12),#increase legend text size
            legend.title = element_blank())  +    #suppress legend title
      annotate("text", x = 0, y = 23, label = "C)", size = 8) +
      scale_color_manual(values = c("red", "blue")) +
      labs(x = expression(paste('Stocking density, ', P[0],' (', Pm^-2, ")", sep = "")), 
           y = "Harvests per 10 years")  +
      scale_y_continuous(limits = c(0, 25),
                         breaks = seq(0,25,5),
                         labels = paste("    ", seq(0,25,5))) +
      scale_x_continuous(limits = c(0, 8),
                         breaks = c(0, 2, 4, 6, 8))  

  eum_crv2
  
  multiplot(eum_crv2, prf_crv2, eum_harvests2, layout = eum.layout)
  
```

```{r save_Fig3_with_uncertainty, include = FALSE}
png("Figures/eum_curve_3panel_uncertainty.png",
    height = 10, width = 8, units = "in",
    res = 300)

  multiplot(eum_crv2, prf_crv2, eum_harvests2, layout = eum.layout)

dev.off()  
```


```{r save_eum_crv, include = FALSE}
eum_sims_all_sum %>% 
    ggplot(aes(x = P_nought/1000, y = cum_Profit_Med/1000, col = Species)) + 
      geom_line(size = 1.25) +
      geom_ribbon(aes(x = P_nought/1000, ymin = cum_Profit_loq/1000, ymax = cum_Profit_upq/1000, fill = Species), alpha = 0.3, size = 0) +
      theme_bw() +
      theme(legend.position = c(0.2, 0.10),        #place legend inside plot
            legend.background = element_rect(fill = "transparent"),
            axis.text = element_text(size = 15),  #increase axis label size
            axis.title = element_text(size = 18), #increase axis title size
            legend.text = element_text(size = 12),#increase legend text size
            axis.title.x = element_blank(),       #Suppress x axis since it shares it with below plot
            axis.text.x = element_blank(),
            legend.title = element_blank())  +    #suppress legend title
      scale_color_manual(values = c("red", "blue")) +
      geom_hline(yintercept = 0, aes(col = grey20)) +
      annotate("text", x = 0, y = 12.5, label = "A)", size = 8) +
      labs(y = expression(paste('10-Year Profits', ' (1000s USD)', sep = "")))  +
      scale_y_continuous(limits = c(-3000, 12750)/1000,
                         breaks = seq(-2.500, 12.500, 2.500),
                         labels = paste("", seq(-2.500, 12.500, 2.500))) +
      scale_x_continuous(limits = c(0, 8),
                         breaks = c(0, 2, 4, 6, 8))

ggsave("Figures/eum_curve_uncertainty.png",
       height = 4, width = 8, units = "in")
```

# Optimal management tables  

Also want a table showing set of parameters and outputs from optimal management. Two approaches here: can either consider the peak *median* cumulative profits from simulations across stocking densities and times as optimal management and draw uncertainty from those simulations, or identify optimal management from parameter point estimates, then estimate uncertainty from LHC parameter sets at that stocking density. Estimates from the latter are reported in the manuscript, but there's not a huge difference between the two.

```{r op_mgmt_table, cache = TRUE}
  #Get optimal stocking parameters considering uncertainty for vollenhovenii
    opt.vol.unc <- eum_sims_vol %>% 
      group_by(P_nought) %>% 
      summarise(Cum_profit_med = median(cum_profits),
                harvest_time_sum = get_sum(time),
                harvest_mass_sum = get_sum(harvest_mass),
                harvest_length_sum = get_sum(L),
                harvest_number_sum = get_sum(P),
                profit_cycle_sum = get_sum(profit),
                roi_sum = get_sum(roi),
                n_harvest_sum = get_sum(n_harvest),
                cum_profit_sum = get_sum(cum_profits)) %>% 
      filter(Cum_profit_med == max(Cum_profit_med))
    
    knitr::kable(t(opt.vol.unc), caption = "Estimates of M. vollenhovenii optimal management (uncertainty during optimization)")

  #Get optimal stocking parameters considering uncertainty for rosenbergii
    opt.ros.unc <- eum_sims_ros %>% 
      group_by(P_nought) %>% 
      summarise(Cum_profit_med = median(cum_profits),
                harvest_time_sum = get_sum(time),
                harvest_mass_sum = get_sum(harvest_mass),
                harvest_length_sum = get_sum(L),
                harvest_number_sum = get_sum(P),
                profit_cycle_sum = get_sum(profit),
                roi_sum = get_sum(roi),
                n_harvest_sum = get_sum(n_harvest),
                cum_profit_sum = get_sum(cum_profits)) %>% 
      filter(Cum_profit_med == max(Cum_profit_med))
    
    knitr::kable(t(opt.ros.unc), caption = "Estimates of M. rosenbergii optimal management (uncertainty during optimization)")

  vol_op_mgmt <- expand.grid.df(lhcpars.aqua, expand.grid(L_nought = opt.vol$L_nought, P_nought = opt.vol$P_nought)) %>% 
    bind_cols(pmap_df(., sim_aqua_eum, species = "M. vollenhovenii")) %>% group_by(P_nought, L_nought) %>% 
    summarise(harvest_time_med = get_sum(time),
              harvest_mass_med = get_sum(harvest_mass),
              harvest_length_med = get_sum(L),
              harvest_number_med = get_sum(P),
              profit_cycle_med = get_sum(profit),
              roi_med = get_sum(roi),
              n_harvest_med = get_sum(n_harvest),
              cum_profit_med = get_sum(cum_profits))

  knitr::kable(t(vol_op_mgmt), caption = "Estimates of M. vollenhovenii optimal management (parametric uncertainty)")

  ros_op_mgmt <- expand.grid.df(lhcpars.aqua, expand.grid(L_nought = opt.ros$L_nought, P_nought = opt.ros$P_nought)) %>% 
    bind_cols(pmap_df(., sim_aqua_eum, species = "M. rosenbergii")) %>% group_by(P_nought, L_nought) %>% 
    summarise(harvest_time_med = get_sum(time),
              harvest_mass_med = get_sum(harvest_mass),
              harvest_length_med = get_sum(L),
              harvest_number_med = get_sum(P),
              profit_cycle_med = get_sum(profit),
              roi_med = get_sum(roi),
              n_harvest_med = get_sum(n_harvest),
              cum_profit_med = get_sum(cum_profits))

  knitr::kable(t(ros_op_mgmt), caption = "Estimates of M. rosenbergii optimal management (parametric uncertainty)")
```
